### 2021-04-07 notes/notes.tex

\section{Simulation results}
\subsection{Effects of observation noise on inference}
Observation noise refers to the noise on the position of the hand. The
generating process is a Gaussian with $\sigma = 0.1$, which is determined in
./code/adaptation/pars.py. However, the agent has a belief on this value, which
is fixed for the agent. This value (obs\_sd, which can be passed on
instanciation) can be used in lieu of an explicit $\Delta t$ parameter which
controls the size of the time step

@@

\begin{tabularx}{\textwidth}{
  >{\hsize=.2\hsize\linewidth=\hsize}X|
  >{\hsize=.1\hsize\linewidth=\hsize}X|
  >{\hsize=.1\hsize\linewidth=\hsize}X|
  l}
% {l|{\hsize=.4\hsize}X|{\hsize=0.3\hsize}X|{\hsize=0.3\hsize}X}
Agent & Obs noise & Cue noise & Notes \\ \hline \hline
LR    & 1.2       & 0.04      & Slow fake-context inference. Maybe the priors coming from the previous stage are messing things up. \\ \hline
1 & 1 & 1 & 1
\end{tabularx}

\section{Conclusions}

>>>>

\section{Simulation results}
\subsection{Deadaptation and context inference}
During the deadaptation phase, not all parametrized agents detect the correct
context. For each agent type (LR, LRS, LRMS), different parameter values allow
the information from the predicted hand positions to overcome the information
from the cue, which enables the correct identification of the current context.

It is unclear which parameter values lead to this, but, as expected, prediction
noise (see XXX) and context noise (see XXX) play an important role. In
particular, keeping the prediction noise below 0.2 seems to be necessary for
the correct identification of the context, for all the used values of context
noise. It could be good to check this.

@@

\begin{tabularx}{\textwidth}{
  >{\hsize=.2\hsize\linewidth=\hsize}X|
  >{\hsize=.1\hsize\linewidth=\hsize}X|
  >{\hsize=.1\hsize\linewidth=\hsize}X|
  l}
% {l|{\hsize=.4\hsize}X|{\hsize=0.3\hsize}X|{\hsize=0.3\hsize}X}
Agent & Obs noise & Cue noise & Notes \\ \hline \hline
LR    & 1.2       & 0.04      & Slow fake-context inference. Maybe the priors coming from the previous stage are messing things up. \\ \hline
1 & 1 & 1 & 1
\end{tabularx}
>>>>>>> adc91ff996e45d6eaf8974cd33ea69b5d380ed07

\subsection{Adaptation}
Adaptation happens mostly very quickly for all agents. For the current $\Delta t = \dt$, adaptation happens within 20 to 30 time steps, although many times (depending on agent and parametrization) it happens much more quickly. For example, for the LR agent with prediction noise of 0.15, cue noise and context noise of 0, and assumed force variability of 0.25, within 15-20 time steps the adaptation is complete.
\section{Conclusions}
